Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-09 paper.tex
High nut causes high turb trans

Turbulent transport and mean streamwise pressure gradient ($-\partial P \partial
x$) terms show the largest discrepancy between results. The 3-D SST case,
despite doing a good job predicting turbulence kinetic energy, significantly
overpredicts the turbulent transport term, while other CFD cases are comparable
with the experiment. This seems to be balanced by a large adverse pressure
gradient, which is also present to a smaller degree in the 3-D SA case.
Interestingly, in contrast, both 2-D CFD cases create a wake where the pressure
gradient is acting to slightly accelerate the flow at $x/D=1$. Unfortunately,
pressure data were not acquired from the experiment, though results from the 3-D
delayed detached eddy simulation (DDES) of Boudreau and Dumas
\cite{Boudreau2015} concur with the adverse pressure gradient condition.

>>>>

Turbulent transport and mean streamwise pressure gradient ($-\partial P \partial
x$) terms show the largest discrepancy between results. The 3-D SST case,
despite doing a good job predicting turbulence kinetic energy, significantly
overpredicts the turbulent transport term, thanks to its high levels of
turbulent viscosity, while other CFD cases are comparable with the experiment.
This seems to be balanced by a large adverse pressure gradient, which is also
present to a smaller degree in the 3-D SA case. Interestingly, in contrast, both
2-D CFD cases create a wake where the pressure gradient is acting to slightly
accelerate the flow at $x/D=1$. Unfortunately, pressure data were not acquired
from the experiment, though results from the 3-D delayed detached eddy
simulation (DDES) of Boudreau and Dumas \cite{Boudreau2015} concur with the
adverse pressure gradient condition.
